% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\setlength{\textheight}{10.2in} % set text height big enough for box
\topmargin=-.5in       % to start box .5in from top of page
\oddsidemargin=-.5in   % to start box .5in from left of page
    
\begin{document}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The following lines define \boxaround, used to draw a box on the page.
% The parameter is the entire text of the resume. Must fit on one page!
%
% \boxaroundhmargin is the left & right margin around the text inside the box.
% \boxaroundvmargin is the top & bottom margin around the text inside the box.
% \boxrulethickness controls thickness of line used to draw the box.
% You can change these 3 things in the lines below:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newdimen\boxrulethickness\newdimen\boxaroundhmargin\newdimen\boxaroundvmargin
\boxrulethickness=.5pt        %controls thickness of line 
\boxaroundhmargin=35pt        % about a half inch
\boxaroundvmargin=40pt        % to fit more text on page, make this smaller
%%%%%%%%%%%%%%%%%%%%%%%%% Don't read this stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hsize=7.5in% \vsize=10.5in             % use bigger dimensions for box
\newbox\MACboxA  \newdimen\MACdimenA
% \borderandboxit is used inside \boxaround:
\def\borderandboxit#1#2#3{\vbox{\hrule height#2\hbox{\vrule width#2\hskip#1\hskip-#2%
  \vbox{\vskip#1\relax#3\vskip#1}\hskip#1\hskip-#2\vrule width#2}\hrule height#2}}
%
\long\def\boxaround#1{\vskip6pt
  {\MACdimenA=\hsize \advance\MACdimenA by-\boxaroundhmargin
   \advance\MACdimenA by-\boxaroundhmargin   % once for each side
   \setbox\MACboxA=\hbox to \hsize{\hskip\boxaroundhmargin%\hss
                     \vbox{\hsize=\MACdimenA
                           \vskip\boxaroundvmargin #1
                           \vskip\boxaroundvmargin}\hss}%
   \borderandboxit{0pt}\boxrulethickness{\box\MACboxA}}%
  \vskip2pt plus0pt minus0pt
}
%%%%%%%%%%%%%%%%%%%  End of \boxaround macro %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\boxaround{ % put the text on the page inside a box  

\name{Robert A. Wagner\\[12pt]}
\address{\bf Present Address\\ 2355 Murray Hill Rd \#430C\\Cleveland, OH 44106\\
        (330) 858-8123\\raw141@case.edu} 
\address{\bf Permanent Address\\2467 Barrington Rd\\
         Fairlawn, OH 44333\\ (330) 836-5546}
        

 
\begin{resume}


\section{\bf  Education}% with postscript font \sl produces bold italic
%                         with default font (CM) \sl produces slanted type
Case Western Reserve University, B.S.,  Computer Science, 
expected May 2019 
 
Copley High School, Graduated with Honors, May 2015 
 
\section{\bf  Related Experience}
\begin{ncolumn}{2}
{\it Undergraduate Research Assistant}  &   8/15-Present 
\end{ncolumn}\\
Kirsch Lab, Case Western Reserve University, Cleveland, OH\\
Part of the BrainGate 2 project. Involved  in  development of goal based algorithms for neural decoding. Used linear discriminant analysis to create classifiers for the purpose of target differentiation based on position of a cursor. Created data visualization tools for easier understanding of path efficiency. Implemented games which responded in real time to neural signals recorded via a Brain- Machine Interface.


\begin{ncolumn}{2} 
{\it Intern} &  7/13 \& 7/14 
\end{ncolumn}\\
Safadi Lab, Department of Anatomy and Neurobiology, Northeast Ohio Medical University, Rootstown, OH \\
Interned under Dr. Fayez Safadi with a focus on research into Osteoblastic differentiation. Performed cell culture and microscopy for the analysis of the effect of electrostimulation on bone growth.

\begin{ncolumn}{2}
{\it Mentor} & 7/14
\end{ncolumn}\\  
Austen BioInnovation Institute, Akron, OH \\
Taught the basics of Biomedical Engineering including computer-aided design, problem identification and solving. Helped a group of students apply the aforementioned skills to develop a product idea for concussion prevention and detection.
 
\section{\bf  Skills}
\textit{Programming languages:} Java, Matlab, Python\\
\textit{Software:} SolidWorks, Microsoft Office\\
\textit{Tools: } Vim, Postgresql, Git, Github, Intellij Idea, Pycharm, Sublime Text

\section{\bf Relevant Courses}
EECS 341: Introduction to Database Systems\\
EECS 340: Algorithms\\
EECS 302: Discrete Mathematics\\
MATH 307: Linear Algebra\\
EECS 233: Introduction to Data Structures\\
\section{\bf  Honors}
SOURCE 2016 Summer Research Scholar\\
National Merit Scholar \\
National Honor Society\\
Source America Design Challenge 2015 Champion

 
\section{\bf  Activities}
Delta Chi Fraternity, Pytte Cup Chair and Judicial Board Member\\
Alpha Phi Omega Fraternity, Sergeant at Arms \\
CWRU Ultimate Frisbee, Developmental Team Member \\
Intramural Soccer, Floor Hockey \\
Other interests include: Running, Soccer, and Reading 


\end{resume}

\vfill} %    end the material being boxed.
\end{document}


